Traditional agroforestry systems in Timor-Leste can store large amounts of carbon in both soil and biomass

### 2024-04-17 manuscript.Rmd
change units in site-soil table: from % into g/kg

@@

```{r tab.id = "site-soil", tab.lp="supp-tab", results = "show", tab.cap.pre="Table S", tab.cap = "Soil characteristics of the sites (depth of 0-30 cm), presented as mean values with 95% confidence intervals (in parentheses). The confidence intervals were calculated by propagating a 12% error on the lab-provided values and obtaining site-level estimates through bootstrapping plot values (1000 simulations). Total organic carbon content (dry combustion method) ; total nitrogen content (dry combustion method) ; pH in water (soil:deionized water ratio of 1:2.5) ; CEC - cation exchangeable capacity - and exchangeable cations (Ca, K, Mg and Na) at soil pH [Cobaltihexamine method; Orsini and Remy, 1976]."}
flextable(
  data_soil_site,
  col_keys = c("site", "CLAY", "silt", "sand", "Corg",
               "N", "Corg_N", "pH", "CEC", "Ca", "K", "Mg", "Na"), 
  cwidth = 0.5
) |> set_header_labels(
  values = c("Site", "Clay (%)", "Silt (%)", "Sand (%)", "SOC content (%)", 
             "N", "C/N", "pH", "CEC", "Ca", "K", "Mg", "Na"))|> 
  compose(i = 1, j = "N", part = "header", value = as_paragraph("N (%", as_sub("o"), ")")) |>
  compose(i = 1, j = "CEC", part = "header", value = as_paragraph( "CEC (cmolc kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "Ca", part = "header", value = as_paragraph( "Ca (cmolc kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "K", part = "header", value = as_paragraph( "K (cmolc kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "Mg", part = "header", value = as_paragraph( "Mg (cmolc kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "Na", part = "header", value = as_paragraph( "Na (cmolc kg", as_sup("-1"), ")"))
```

>>>>

# convert sand, silt, clay and C content from % into g/kg
data_soil_site_simu[ variable %in% c("Corg", "CLAY", "sand", "silt"), value := value*10]

@@

```{r tab.id = "site-soil", tab.lp="supp-tab", results = "show", tab.cap.pre="Table S", tab.cap = "Soil characteristics of the sites (depth of 0-30 cm), presented as mean values with 95% confidence intervals (in parentheses). The confidence intervals were calculated by propagating a 12% error on the lab-provided values and obtaining site-level estimates through bootstrapping plot values (1000 simulations). Total organic carbon content (dry combustion method) ; total nitrogen content (dry combustion method) ; pH in water (soil:deionized water ratio of 1:2.5) ; CEC - cation exchangeable capacity - and exchangeable cations (Ca, K, Mg and Na) at soil pH [Cobaltihexamine method; Orsini and Remy, 1976]."}
flextable(
  data_soil_site,
  col_keys = c("site", "CLAY", "silt", "sand", "Corg",
               "N", "Corg_N", "pH", "CEC", "Ca", "K", "Mg", "Na"), 
  cwidth = c(0.5, rep(0.6, 5), rep(0.5, 2), rep(0.6, 5)) 
) |> 
  compose(i = 1, j = "CLAY", part = "header", value = as_paragraph("Clay\n(g kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "silt", part = "header", value = as_paragraph("Silt (g kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "sand", part = "header", value = as_paragraph("Sand (g kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "Corg", part = "header", value = as_paragraph("C content (g kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "N", part = "header", value = as_paragraph("N content (g kg", as_sup("-1"), ")")) |>
  compose(i = 1, j = "Corg_N", part = "header", value = as_paragraph("C/N")) |> 
  compose(i = 1, j = "CEC", part = "header", value = as_paragraph( "CEC (cmolc kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "Ca", part = "header", value = as_paragraph( "Ca (cmolc kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "K", part = "header", value = as_paragraph( "K (cmolc kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "Mg", part = "header", value = as_paragraph( "Mg (cmolc kg", as_sup("-1"), ")")) |> 
  compose(i = 1, j = "Na", part = "header", value = as_paragraph( "Na (cmolc kg", as_sup("-1"), ")"))
```
